Exact asymptotic expressions for local clustering in hyperbolic random graphs \\ \TM{ I prefer not to use the term ``hyperbolic random graph". Better : KPKVB random graph or, in the title,``a hyperbolic model of complex networks"}

### 2019-01-19 concentration_argument.tex
Performed the splitting of cases for k and responded to/implemented several comments from Tobias.

Many of the computations in this paper will involve integrals whose integrand contains $\Prob{\Po(\mu_n(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and $\mu_n(y) \approx e^{y/2}$. For instance, the expected modified local clustering function $c_\infty(k)$ in $G_\Pcal$ equals
\[
	\frac{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} \Delta_{\Pcal}(y) \alpha e^{-\alpha y} \dd y}
	{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} \alpha e^{-\alpha y} \dd y},
\]
where $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$. 
\TM{ Maybe state where $\Delta$ is defined in the paper. }

@@

\subsection{Concentration \TM{ "of heights"? } argument for the infinite model}

Recall that $\rho(y, k)$ is the probability density function of a Poisson random variable with expectation $\mu_{\alpha, \nu}(B_\Pcal(y)) = \xi_{\alpha,\nu}e^{\frac{y}{2}}$. 
For any sequence $\{k_n\}_{n \ge 1}$, possibly constant, define
\begin{equation}\label{eq:def_kappa_n}
	\kappa_n := \begin{cases}
		\log(n) &\mbox{if } k_n = \bigT{1},\\
		\sqrt{k_n \log(k_n)} &\mbox{else.}
	\end{cases}
\end{equation}
\TM{ This is not a good definition. There are sequences that neither stay bounded nor tend to infinity, e.q.~odd values equal to 2 even values equal to $\log n$. How do you decide for a given $k_n$ which of the two cases you pick. To solve this we could either restrict to sequences that are either a) constant or b) tending to infinity; or we could make a cut-off at some specific, slow growing function such as $\log\log\log n$. }
and define further, for any $C > 0$
\begin{equation}\label{eq:def_K_C_set}
	\Kcal_C(k_n) = \left\{p=(x,y) \in \R \times \R_+ : \frac{k_n - C \kappa_n}{\xi_{\alpha,\nu}} \vee 0 \le e^{\frac{y}{2}}
	\le \frac{k_n + C \kappa_n}{\xi_{\alpha,\nu}} \wedge e^{R_n/2} \right\},
\end{equation}
\TM{ taking max with 0 and min with $R$ do not seem necessary. }
Where we recall that $a \vee b = \max\{a,b\}$ and $a \wedge b = \min\{a,b\}$.

Note that if $k_n = \Omega(\log(n))$ then $e^{y/2} = \bigT{k_n}$ whenever $p=(x,y) \in \Kcal_C(k_n)$. The next lemma states that for a large class of functions $h(y)$, to compute the integral 
\[
	\int_{\Rcal_n} \rho(y,k_n) h(y) f_{\alpha,\nu}(x,y) \dd x \dd y
\]
\TM{ This part is supposed to be for the infinite model, yet you integrate over the finite box $\Rcal_n$. Is this really meant?
I would have expected we just integrate wrt.~$y$ and replace $f_{\alppha,\nu}(x,y)$ by $\alpha e^{-\alpha y}$, the exponential density.}
it is enough to consider integration \BL{over} $\Kcal_C(k_n)$ instead of $\Rcal_n$. More precisely, for any $\ell_n = (1 + \smallO{1})k_n$ it is enough to consider $\Kcal_C(\ell_n)$. The flexibility of using $(1+\smallO{1})k_n$ instead of $k_n$ will prove useful in later sections.

\begin{lemma}\label{lem:concentration_argument}
Let $\alpha > \frac{1}{2}$, $\nu > 0$, $\{k_n\}_{n \ge 1}$ be any positive sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$ and let $\ell_n = k_n(1 + \epsilon_n)$, with $\epsilon_n \to 0$. In addition let $\beta < \alpha$ and $h : \R_+ \rightarrow  \R$ be a any function such that $h(y) = g(y)e^{\beta y}$ with $|g(y)|$ uniformly bounded on $\R_+$. Then, if we define for $C > 0$
\[
	\lambda_n^\pm = \ell_n \pm C \kappa_n, 
	\quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right),
\] 
\TM{ If $k$ is constant, then $\ell^- < 0$ and hence 
$a^-$ is undefined! Need to change the definitions. }

we have
\begin{equation}\label{eq:error_bound_int_rho_not_K}
\begin{aligned}
	\int_{\R_+ \setminus [a_n^-, a_n^+]} \rho(y,k_n) h(y) \alpha e^{-\alpha y} \dd x \dd y
	&= \begin{cases}
		\bigO{\log(n)^{k_n} n^{-\frac{C}{2}}} &\mbox{if } k_n = \bigT{1} \\
		\bigO{k_n^{-(1+C^2)/2}} &\mbox{else.}
	\end{cases}
\end{aligned}
\end{equation}
\TM{ As before, this is not a proper dichotomy. (unless we assume more about the sequences $k_n$, i.e.~either constant or tending to infinity }
as $n \to \infty$.

@@

\subsection{Average degree in the hyperbolic random graph}\label{ssec:average_degree_HP_n}

\TM{  the term ``average degree" does not fit very well with what goes on in this section. We are considering the expected number of points in a ball, but not yet computing the average degree of the graph. }
Recall that under the coupling between the hyperbolic random graph and the finite box model $|x-x^\prime|_{\pi e^{R_n/2}} \le \Omega(r,r^\prime)$, while the coupling lemma (Lemma~\ref{lem:asymptotics_Omega_hyperbolic}) gives that  
\[
	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R_n} \leq \Omega(r, r^\prime) 
		\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R_n},
\]
for $y + y^\prime < R_n$. \TM{ Say what $K$ is and what the restrictions on $r, r'$ are. } This result enables us to determine the measure of a ball around a given point $p=(0,y)$ which will be fairly useful in our subsequent analysis.

\begin{lemma}\label{lem:average_degree_hyperbolic}
Let $\eps \in (0, 1)$. Then for all $0 \le y \le (1 - \eps)R_n$
\[
	 1 - \phi_{\H,n}^{(1)}(y) - \phi_{\H,n}^{(2)}(y) \le \frac{\Mu{\BallHyp{0,y}}}{\Mu{\BallPo{0,y}}} 
	 \le 1 - \phi_{\H,n}^{(1)}(y) + \phi_{\H,n}^{(2)}(y),
\]
\TM{ maybe remind the reader just before of the rather counter intuitive definition of $\BallHyp{0,y}$, which 
lives in the box model not in the original hyperbolic disk. }
where
\[
	\phi_{\H,n}^{(1)}(y) = \frac{2\alpha - 1 - 4\pi}{4\pi} e^{-(\alpha - \frac{1}{2})(R_n - y)} 
		+ \left(\alpha - \frac{1}{2}\right)\pi e^{-(\alpha - \frac{1}{2})R_n - y/2},
\]
and
\[
	\phi_{\H,n}^{(2)}(y) = 
	+ \begin{cases}
			\frac{(2\alpha - 1)K}{3 - 2\alpha}\left(e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(R_n - y)}\right)
			&\mbox{if } 1/2 < \alpha < 3/2,\\
			\frac{(2\alpha -1)K}{2} (R_n - y)e^{-(R_n - y)} &\mbox{if } \alpha = 3/2,\\
			\frac{(2\alpha - 1)K}{2\alpha - 3} \left(e^{-(R_n - y)} - e^{-(\alpha - \frac{1}{2})(R_n - y)}\right)
			&\mbox{if } \alpha > 3/2.
		\end{cases}
\]
\TM{ We want to say in the lemma where $K$ comes from. (not everyone reads surrounding text, or reads linearly, in a paper as long as this one.) }
\end{lemma}

\begin{proof}
We will split the computation of $\Mu{\BallHyp{0,y}}$ into the cases $y^\prime > R_n - y$ and $y^\prime \le R_n - y$ \TM{ You have not said what $y^\prime$ is! } where for the latter we utilize Lemma~\ref{lem:asymptotics_Omega_hyperbolic}. Recall that $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$ where $\xi_{\alpha,\nu} = \frac{4\alpha\nu}{\pi(2\alpha - 1)}$.

@@

\subsection{Average degree in the finite box model}\label{ssec:average_degree_P_n}

\TM{ same comment Re: average degree. }
For the finite box model $G_{\Pcal,n}(\alpha, \nu)$ we obtain a similar result for the average degree.

\begin{lemma}\label{lem:average_degree_P_n}
For all $p \in \Rcal_n$, such that $y > 2\log(\pi/2)$,
\[
	\mu_{\alpha,\nu}(B_{\Pcal,n}(p)) = \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - \phi_n(y)\right)
\]
\TM{ where did the curly B's go? }
where $\phi_n(y) \ge 0$ is given by
\[
	\phi_n(y) = \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)}e^{-(\alpha-\frac{1}{2})(R_n - y)}
	- \frac{(2\alpha - 1)\pi}{4\alpha}\left(\left(\frac{\pi}{2}\right)^{-2\alpha} 
	e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(\alpha - \frac{1}{2})R_n - \frac{y}{2}}\right).
\]
On the other hand, if $y \le 2 \log(\pi/2)$ then
\[
	\mu_{\alpha,\nu}(B_{\Pcal,n}(p)) = \mu_{\alpha,\nu}(B_\Pcal(p))\left(1 - e^{-(\alpha - \frac{1}{2})R_n}\right).
\]
\end{lemma}

\begin{proof}
First note that since we have identified the boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ we can assume, without loss of generality, that $p = (0,y)$. We then have that
\[
	\BallPon{p} = \left\{p^\prime \in \Rcal_n \, : \, |x^\prime| \le e^{\frac{y + y^\prime}{2}}\right\},
\] 
\TM{ There a rogue subscript $n$ in $|x'|_n$ }
whose boundaries given by the equations $x^\prime = \pm e^{\frac{y+y^\prime}{2}}$ intersect the left and right boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ at height
\TM{ weird sentence }
\[
	h(y) = R_n + 2 \log\left(\frac{\pi}{2}\right) - y.
\]
Therefore, if $y \le 2 \log(\pi/2)$ this intersection occurs above the height $R_n$ of the box $\Rcal_n$ while in the other case the full region of the box above $h(y)$ is connected to $p$.

@@

\subsection{Concentration \TM{ OF HEIGHTS? }argument for hyperbolic and finite box model}

With the results on the average degrees in the two finite Poisson models, we can now establish a result that allows us to extend the concentration argument to the case where instead of $\rho(y,k)$ we consider the degree distributions $\rho_{\HP,n}(y,k)$ and $\rho_{n}(y,k)$ in $G_{\HP,n}$ and $G_{\Pcal,n}$, respectively. The lemma is stated in a more general form, to make it applicable to slightly other cases later in the paper. To understand the general conditions presented in the statement of the lemma we write $\mu_n(y) = \Mu{\BallPon{y}}$ and $\mu(y) = \Mu{\BallPo{y}}$ and recall the result from Lemma~\ref{lem:average_degree_P_n}
\[
	\mu_n(y) = \mu(y)(1 - \phi_n(y)).
\]
For the error function $\phi_n(y)$ we note that for any $0 < \varepsilon < 1$, as $n \to \infty$, 
\[
	\sup_{0 \le y \le (1-\varepsilon)R_n} \phi_n(y) = \smallO{1},
\]
while
\[
	\frac{\partial \phi_n(y)}{\partial y} = \bigT{\phi_n(y)}.
\]
These are exactly the crucial properties of the error function that allow for a concentration argument. Moreover, if the integrand also contains a function $g_n(y)$ that is reasonably nice, we can replace the $\rho_{n}(y,k_n)$ in the integrand by $\rho(y,k_n)$. In particular, the triangle counting function $\Delta_{\Pcal}(y)$ will satisfy these conditions, see Section~\ref{sec:clustering_Pn_to_P}.

\begin{lemma}\label{lem:concentration_argument_rho_approximation}
Let $\alpha > \frac{1}{2}, \nu > 0$, $k_n$ be any positive sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and let $\Kcal_{C}(\ell_n)$ be defined as in~\eqref{eq:def_K_C_set}. In addition, define $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ is any function satisfying 
\[
	\Mu{\BallPo{0,y}}(1 - \phi_n^{(1)}(y)) \le \hat{\mu}_n(y) \le \Mu{\BallPo{0,y}}(1 + \phi_n^{(2)}(y))
\]
where $\phi_n^{(i)} : \R_+ \to \R_+$ are such that $\sup_{0 \le y \le (1-\varepsilon)R_n} \phi_n(y)^{(i)} = \smallO{1}$ for any $0 < \varepsilon < 1$ and $\partial \phi_n^{(i)}(y)/\partial y = \bigT{\phi_n^{(i)}(y)}$. Then the following holds for some $C > 0$ large enough:
\begin{enumerate}
\item for any sequence of functions $h_n(y) : \R_+ \to \R$ such that $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s e^{\beta y}}$ \TM{ Why not adjust $h$ so that we incorporate $\hat\rho$ in line below. Then both items look more similar. }  for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$, we have,
\[
	\int_{\Rcal_n} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y 
	= (1 + o(1)) \int_{\Kcal_{C}(\ell_n)} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
\]
\item for any uniformly bounded function $h : \R_+ \to \R$,
\[
	\int_{\Rcal_n} h(y) \hat{\rho}_n(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y 
	= (1 + o(1)) \int_{\Rcal_n} \rho(y,k_n) h(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
\]
\end{enumerate}
\TM{ Say in the lemma statement where def of $K_C$ can be found. }
\end{lemma}

\begin{proof}
Similarly to the proof of Lemma~\ref{lem:concentration_argument} we define 
\[
	\lambda_n^\pm = \ell_n \pm C \kappa_n, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right).
\] 
\TM{ Same problem as in L3.1. $\lambda^-$ can be negative, in which case $a^-$ is undefined.}
In addition we fix $\varepsilon > 0$ such that $\varepsilon < \min\{1- \frac{s}{2\alpha(2\alpha + 1)}, 1\}$. Then since $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s}$ we have
\begin{align*}
	k_n^s \int_{(1-\varepsilon)R_n}^{R_n} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
	&= \bigO{1} \hat{\rho}_n((1-\varepsilon)R_n,k_n) k_n^s e^{-\alpha(1-\varepsilon)R_n} \\
	&= \bigO{\hat{\rho}_n((1-\varepsilon)R_n,k_n) k_n^s n^{-2\alpha(1 - \varepsilon)}} \\
	&= \smallO{ \hat{\rho}_n((1-\varepsilon)R_n,k_n) n^{\frac{s}{2\alpha + 1} - 2\alpha(1-\varepsilon)}} = \smallO{1},
\end{align*}
where the last step follows by our choice of $\varepsilon$. Hence it is enough to prove both statement on $\Rcal_n((1-\varepsilon)R_n, R_n)$ instead of $\Rcal_n$.
\PvdH{@All: This is where we use that $s < 2\alpha(2\alpha + 1)$. I think this can be removed by using a more careful bound but I am not sure this is needed.}

>>>>

Many of the computations in this paper will involve integrals whose integrand contains the function $\Prob{\Po(\mu_n(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and $\mu_n(y) \approx e^{y/2}$. For instance, the expected modified local clustering function $c_\infty(k)$ in $G_\Pcal$ equals
\[
	\frac{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} \Delta_{\Pcal}(y) \alpha e^{-\alpha y} \dd y}
	{\int_0^\infty \Prob{\Po(\Mu{\BallPo{0,y}}) = k} \alpha e^{-\alpha y} \dd y},
\]
where $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$ and $\Delta_{\Pcal}(y)$ is defined by~\eqref{eq:def_delta_p}.

@@

\subsection{Concentration of heights argument for the infinite model}

Recall that $\rho(y, k)$ is the probability density function of a Poisson random variable with expectation $\mu_{\alpha, \nu}(B_\Pcal(y)) = \xi_{\alpha,\nu}e^{\frac{y}{2}}$. 
For any sequence $\{k_n\}_{n \ge 1}$, possibly constant, define
\begin{equation}\label{eq:def_kappa_n}
	\kappa_n := \begin{cases}
		\log(n) &\mbox{if } k_n = \bigT{1},\\
		\sqrt{k_n \log(k_n)} &\mbox{else.}
	\end{cases}
\end{equation}
\TM{ This is not a good definition. There are sequences that neither stay bounded nor tend to infinity, e.q.~odd values equal to 2 even values equal to $\log n$. How do you decide for a given $k_n$ which of the two cases you pick. To solve this we could either restrict to sequences that are either a) constant or b) tending to infinity; or we could make a cut-off at some specific, slow growing function such as $\log\log\log n$. }\PvdH{You are right, I overlooked this fact. I would opt to go with the setting where we consider only sequences that are either asymptotically bounded or tend to infinity. After the new proves are added we can see where we specify this.}
and define further, for any $C > 0$
\begin{equation}\label{eq:def_K_C_set}
	\Kcal_C(k_n) = \left\{p=(x,y) \in \R \times \R_+ : \frac{k_n - C \kappa_n}{\xi_{\alpha,\nu}} \le e^{\frac{y}{2}}
	\le \frac{k_n + C \kappa_n}{\xi_{\alpha,\nu}} \right\},
\end{equation}
Where we recall that $a \vee b = \max\{a,b\}$ and $a \wedge b = \min\{a,b\}$.

Note that if $k_n = \Omega(\log(n))$ then $e^{y/2} = \bigT{k_n}$ whenever $p=(x,y) \in \Kcal_C(k_n)$. The next lemma states that for a large class of functions $h(y)$, to compute the integral 
\[
	\int_{\Rcal_n} \rho(y,k_n) h(y) f_{\alpha,\nu}(x,y) \dd x \dd y
\]
\TM{ This part is supposed to be for the infinite model, yet you integrate over the finite box $\Rcal_n$. Is this really meant?
I would have expected we just integrate wrt.~$y$ and replace $f_{\alpha,\nu}(x,y)$ by $\alpha e^{-\alpha y}$, the exponential density.}\PvdH{I understand this confusion and agree that your suggestion makes more sense here. However, I choose this setup to minimize notations later. I am for changing the setup to what you are suggesting but I will have to spend some time first on checking how that will effect the definitions in later sections.}
it is enough to consider integration \BL{over} $\Kcal_C(k_n)$ instead of $\Rcal_n$. More precisely, for any $\ell_n = (1 + \smallO{1})k_n$ it is enough to consider $\Kcal_C(\ell_n)$. The flexibility of using $(1+\smallO{1})k_n$ instead of $k_n$ will prove useful in later sections.

\begin{lemma}\label{lem:concentration_argument}
Let $\alpha > \frac{1}{2}$, $\nu > 0$, $\{k_n\}_{n \ge 1}$ be any positive sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$ and let $\ell_n = k_n(1 + \epsilon_n)$, with $\epsilon_n \to 0$. In addition let $\beta < \alpha$ and $h : \R_+ \rightarrow  \R$ be a any function such that $h(y) = g(y)e^{\beta y}$ with $|g(y)|$ uniformly bounded on $\R_+$. Then, if we define for $C > 0$
\[
	\lambda_n^\pm = (\ell_n \pm C \kappa_n) \wedge \kappa_n, 
	\quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right),
\] 
\TM{ If $k$ is constant, then $\ell^- < 0$ and hence 
$a^-$ is undefined! Need to change the definitions. }\PvdH{You are right. I changed it by taking the minimum with $\kappa_n$.}

we have
\begin{equation}\label{eq:error_bound_int_rho_not_K}
\begin{aligned}
	\int_{\Rcal_n\setminus \Kcal_{C}(k_n)} \rho(y,k_n) h(y) \alpha e^{-\alpha y} \dd x \dd y
	&= \begin{cases}
		\bigO{\log(n)^{k_n} n^{-\frac{C}{2}}} &\mbox{if } k_n = \bigT{1} \\
		\bigO{k_n^{-(1+C^2)/2}} &\mbox{else.}
	\end{cases}
\end{aligned}
\end{equation}
\TM{ As before, this is not a proper dichotomy. (unless we assume more about the sequences $k_n$, i.e.~either constant or tending to infinity }
as $n \to \infty$.

@@

\subsection{Expected number of points in balls in the hyperbolic random graph}\label{ssec:average_degree_HP_n}

\TM{  the term ``average degree" does not fit very well with what goes on in this section. We are considering the expected number of points in a ball, but not yet computing the average degree of the graph. }\PvdH{I agree and have changed the header.}
Recall that under the coupling between the hyperbolic random graph and the finite box model, for two points $p, p^\prime$ with $y + y^\prime < R_n$, $p^\prime \in \BallHyp{p}$ exactly when $|x-x^\prime|_{\pi e^{R_n/2}} \le \Phi(r,r^\prime)$. In this setting, the coupling lemma (Lemma~\ref{lem:asymptotics_Omega_hyperbolic}) gives that  
\[
	e^{\frac{1}{2}(y+y^\prime)} - K e^{\frac{3}{2}(y+y^\prime) - R_n} \leq \Phi(r, r^\prime) 
		\leq  e^{\frac{1}{2}(y+y^\prime)} + K e^{\frac{3}{2}(y+y^\prime) - R_n},
\]
for some constant $K$. %\TM{ Say what $K$ is and what the restrictions on $r, r'$ are. } 
This result enables us to determine the measure of a ball around a given point $p=(0,y)$ which will be fairly useful in our subsequent analysis. Recall that the hyperbolic ball $\BallHyp{p}$ is a subset of $\Rcal_n$ and not of the hyperbolic disc $\Dcal_{R_n}$, i.e. the balls $\BallHyp{p}$ "live" in the finite box and not the hyperbolic disc.

\begin{lemma}\label{lem:average_degree_hyperbolic}
Let $\eps \in (0, 1)$. Then for all $0 \le y \le (1 - \eps)R_n$
\[
	 1 - \phi_{\H,n}^{(1)}(y) - \phi_{\H,n}^{(2)}(y) \le \frac{\Mu{\BallHyp{0,y}}}{\Mu{\BallPo{0,y}}} 
	 \le 1 - \phi_{\H,n}^{(1)}(y) + \phi_{\H,n}^{(2)}(y),
\]
where
\[
	\phi_{\H,n}^{(1)}(y) = \frac{2\alpha - 1 - 4\pi}{4\pi} e^{-(\alpha - \frac{1}{2})(R_n - y)} 
		+ \left(\alpha - \frac{1}{2}\right)\pi e^{-(\alpha - \frac{1}{2})R_n - y/2},
\]
and
\[
	\phi_{\H,n}^{(2)}(y) = 
	+ \begin{cases}
			\frac{(2\alpha - 1)K}{3 - 2\alpha}\left(e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(R_n - y)}\right)
			&\mbox{if } 1/2 < \alpha < 3/2,\\
			\frac{(2\alpha -1)K}{2} (R_n - y)e^{-(R_n - y)} &\mbox{if } \alpha = 3/2,\\
			\frac{(2\alpha - 1)K}{2\alpha - 3} \left(e^{-(R_n - y)} - e^{-(\alpha - \frac{1}{2})(R_n - y)}\right)
			&\mbox{if } \alpha > 3/2,
		\end{cases}
\]
with $K$ being the constant coming from the approximation of $\Phi$ in Lemma~\ref{lem:asymptotics_Omega_hyperbolic}.
%\TM{ We want to say in the lemma where $K$ comes from. (not everyone reads surrounding text, or reads linearly, in a paper as long as this one.) }
\end{lemma}

\begin{proof}
We perform the computation of $\Mu{\BallHyp{0,y}}$ by splitting the integration with respect to the height $y^\prime$ into the cases $y^\prime > R_n - y$ and $y^\prime \le R_n - y$, %\TM{ You have not said what $y^\prime$ is! } 
where for the latter we utilize Lemma~\ref{lem:asymptotics_Omega_hyperbolic}. Recall that $\Mu{\BallPo{0,y}} = \xi_{\alpha,\nu} e^{y/2}$ where $\xi_{\alpha,\nu} = \frac{4\alpha\nu}{\pi(2\alpha - 1)}$.

@@

\subsection{Expected number of points in balls in the finite box model}\label{ssec:average_degree_P_n}

%\TM{ same comment Re: average degree. }
For the finite box model $G_{\Pcal,n}(\alpha, \nu)$ we obtain a similar result for the average degree.

\begin{lemma}\label{lem:average_degree_P_n}
For all $p \in \Rcal_n$, such that $y > 2\log(\pi/2)$,
\[
	\mu_{\alpha,\nu}(\BallPon{p}) = \mu_{\alpha,\nu}(\BallPo{p})\left(1 - \phi_n(y)\right)
\]
\TM{ where did the curly B's go? }\PvdH{Typo. Fixed}
where $\phi_n(y) \ge 0$ is given by
\[
	\phi_n(y) = \left(\frac{\pi}{2}\right)^{-(2\alpha - 1)}e^{-(\alpha-\frac{1}{2})(R_n - y)}
	- \frac{(2\alpha - 1)\pi}{4\alpha}\left(\left(\frac{\pi}{2}\right)^{-2\alpha} 
	e^{-(\alpha - \frac{1}{2})(R_n - y)} - e^{-(\alpha - \frac{1}{2})R_n - \frac{y}{2}}\right).
\]
On the other hand, if $y \le 2 \log(\pi/2)$ then
\[
	\mu_{\alpha,\nu}(\BallPon{p}) = \mu_{\alpha,\nu}(\BallPo{p})\left(1 - e^{-(\alpha - \frac{1}{2})R_n}\right).
\]
\end{lemma}

\begin{proof}
First note that since we have identified the boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ we can assume, without loss of generality, that $p = (0,y)$. We then have that the boundaries of $\BallPon{p}$ are given by the equations $x^\prime = \pm e^{\frac{y+y^\prime}{2}}$, which intersect the left and right boundaries of $[-\frac{\pi}{2}e^{\frac{R_n}{2}}, \frac{\pi}{2}e^{\frac{R_n}{2}}]$ at height
\[
	h(y) = R_n + 2 \log\left(\frac{\pi}{2}\right) - y.
\]
Therefore, if $y \le 2 \log(\pi/2)$ this intersection occurs above the height $R_n$ of the box $\Rcal_n$ while in the other case the full region of the box above $h(y)$ is connected to $p$.

@@

\subsection{Concentration of heights argument for hyperbolic and finite box model}

With the results on number of points in the balls in the two finite Poisson models $G_{\HP,n}$ and $G_{\Pcal,n}$, we can now establish a result that allows us to extend the concentration argument to the case where instead of $\rho(y,k)$ we consider the functions $\rho_{\HP,n}(y,k)$ and $\rho_{n}(y,k)$. The lemma is stated in a more general form, to make it applicable to slightly other cases later in the paper. To understand the general conditions presented in the statement of the lemma we write $\mu_n(y) = \Mu{\BallPon{y}}$ and $\mu(y) = \Mu{\BallPo{y}}$ and recall the result from Lemma~\ref{lem:average_degree_P_n}
\[
	\mu_n(y) = \mu(y)(1 - \phi_n(y)).
\]
For the error function $\phi_n(y)$ we note that for any $0 < \varepsilon < 1$, as $n \to \infty$, 
\[
	\sup_{0 \le y \le (1-\varepsilon)R_n} \phi_n(y) = \smallO{1},
\]
while
\[
	\frac{\partial \phi_n(y)}{\partial y} = \bigT{\phi_n(y)}.
\]
These are exactly the crucial properties of the error function that allow for a concentration argument. Moreover, if the integrand also contains a function $g_n(y)$ that is reasonably nice, we can replace the $\rho_{n}(y,k_n)$ in the integrand by $\rho(y,k_n)$. In particular, the triangle counting function $\Delta_{\Pcal}(y)$ will satisfy these conditions, see Section~\ref{sec:clustering_Pn_to_P}.

\begin{lemma}\label{lem:concentration_argument_rho_approximation}
Let $\alpha > \frac{1}{2}, \nu > 0$, $k_n$ be any positive sequence such that $k_n = o(n^{\frac{1}{2\alpha + 1}})$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and let $\Kcal_{C}(\ell_n)$ be defined as in~\eqref{eq:def_K_C_set}. In addition, define $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ is any differentiable function satisfying 
\[
	\Mu{\BallPo{0,y}}(1 - \phi_n^{(1)}(y)) \le \hat{\mu}_n(y) \le \Mu{\BallPo{0,y}}(1 + \phi_n^{(2)}(y))
\]
where $\phi_n^{(i)} : \R_+ \to \R_+$ are such that $\sup_{0 \le y \le (1-\varepsilon)R_n} \phi_n(y)^{(i)} = \smallO{1}$ for any $0 < \varepsilon < 1$ and $\partial \phi_n^{(i)}(y)/\partial y = \bigT{\phi_n^{(i)}(y)}$. Then the following holds for some $C > 0$ large enough:
\begin{enumerate}
\item for any sequence of continuous functions $h_n(y) : \R_+ \to \R$ such that $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s e^{\beta y}}$ \TM{ Why not adjust $h$ so that we incorporate $\hat\rho$ in line below. Then both items look more similar. }\PvdH{I am not sure what you are suggesting. Could you explain a bit more?}  for some $s < 2\alpha(2\alpha + 1)$ and $\beta < \alpha$, we have,
\[
	\int_{\Rcal_n} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y 
	= (1 + o(1)) \int_{\Kcal_{C}(\ell_n)} h_n(y) f_{\alpha,\nu}(x,y) \dd x \dd y,
\]
with $\Kcal_{C}$ defined in~\eqref{eq:def_K_C_set}
\item for any continuous and uniformly bounded function $h : \R_+ \to \R$,
\[
	\int_{\Rcal_n} h(y) \hat{\rho}_n(y,k_n) f_{\alpha,\nu}(x,y) \dd x \dd y 
	= (1 + o(1)) \int_{\Rcal_n} \rho(y,k_n) h(y) f_{\alpha,\nu}(x,y) \dd x \dd y.
\]
\end{enumerate}
%\TM{ Say in the lemma statement where def of $K_C$ can be found. }
\end{lemma}

\begin{proof}
Similarly to the proof of Lemma~\ref{lem:concentration_argument} we define 
\[
	\lambda_n^\pm = (\ell_n \pm C \kappa_n) \wedge \kappa_n, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi_{\alpha,\nu}}\right).
\] 
%\TM{ Same problem as in L3.1. $\lambda^-$ can be negative, in which case $a^-$ is undefined.}
In addition we fix $\varepsilon > 0$ such that $\varepsilon < \min\{1- \frac{s}{2\alpha(2\alpha + 1)}, 1\}$. Then since $h_n(y) = \hat{\rho}_n(y,k_n) \bigO{k_n^s}$ we have
\begin{align*}
	k_n^s \int_{(1-\varepsilon)R_n}^{R_n} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
	&= \bigO{1} \hat{\rho}_n((1-\varepsilon)R_n,k_n) k_n^s e^{-\alpha(1-\varepsilon)R_n} \\
	&= \bigO{\hat{\rho}_n((1-\varepsilon)R_n,k_n) k_n^s n^{-2\alpha(1 - \varepsilon)}} \\
	&= \smallO{ \hat{\rho}_n((1-\varepsilon)R_n,k_n) n^{\frac{s}{2\alpha + 1} - 2\alpha(1-\varepsilon)}} = \smallO{1},
\end{align*}
where the last step follows by our choice of $\varepsilon$. Hence it is enough to prove both statement on $\Rcal_n((1-\varepsilon)R_n, R_n)$ instead of $\Rcal_n$.
\PvdH{@All: This is where we use that $s < 2\alpha(2\alpha + 1)$. I think this can be removed by using a more careful bound but I am not sure this is needed.}
